---
title: "Introduction to xaringan"
subtitle: "Beautiful presentations with xaringan"
author: "Alexander Keth"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: ["libs/alketh.css", "libs/remark/default-fonts.css"]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

layout: true
class: my-slide

--- 

## This is the heading

```{r, eval=FALSE}
library("ggplot2")

ggplot(mtcars, aes(x = mpg, y = wt)) +
  geom_point()
```

test 2

---

layout: false
class: split, middle, center

# Your turn!

<div class="highlight-line"></div>

## Do Stuff!

`1+1`, `sum(1:10) + min(1:10)`

```{r, echo=FALSE}
library("ggplot2")

ggplot(mtcars, aes(x = mpg, y = wt)) +
  geom_point()
```

---

layout:true
class: my-slide

---

## a

s

---

## Another slide

text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. 

---

layout:false
class: final-slide, center, middle

# Thanks!

## You can find me at:

<a href="mailto:alexander.keth@uni-hamburg.de">alexander.keth@uni-hamburg.de

<a href="http://github.com/alketh">@alketh

