---
title: "Introduction to xaringan"
subtitle: "Beautiful presentations with xaringan"
author: "Alexander Keth"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: ["libs/alketh.css", "libs/remark/default-fonts.css"]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

layout: true

<div class="rect-top"></div>
<div class="rect-bottom"></div> 

---

## This is the heading

```{r, echo=FALSE}
cat(stringi::stri_rand_lipsum(3, start_lipsum = TRUE), sep="\n\n")
```


```{r}
library("ggplot2")

ggplot(mtcars, aes(x = mpg, y = wt)) +
  geom_point()
```

---

layout: false
class: split, middle, center

# Your turn!

<div class="highlight-line"></div>

## Do Stuff!

`1+1`, `sum(1:10) + min(1:10)`

```{r, echo=FALSE}
library("ggplot2")

ggplot(mtcars, aes(x = mpg, y = wt)) +
  geom_point()
```

---

layout: true

<div class="header"></div>
<div class="footer"></div> 

---

## a

s

---

## Another slide

text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text. text lots of text.

---

layout:false
class: final-slide, center, middle

# Thanks!

## You can find me at:

<a href="mailto:alexander.keth@uni-hamburg.de">alexander.keth@uni-hamburg.de

<a href="http://github.com/alketh">@alketh

